<br>
<br>
<p>
<iframe src="https://easytoremember.shinyapps.io/DC_Crime_Map/" style="border: none; width: 100%; height: 450px"></iframe>
</p>
<br>
<br>
<table style="height: 100%;" width="100%" cellpadding="5px">
<tbody>
<tr>
<td>
<center>
<p style="text-align: justify; width: 600px;">
The map you see above is an interactive map illustrating every reported crime occurred in the month of January, 2016. You will see a lot of these interactive graphic tools on my blog. In case you're wondering what coding program I am using to generate these maps, my foundation is mainly R. But, I must add that although R is handy dandy, I generate many maps using various external packages such as ArcGIS and Shiny App. I use external packages because writing a script for each and every element is for one, out of my abilities (I'm considered a noob in the computer industry), and two, it doesn't make sense to create something when something better is already out in the market.</p>
</center>
</td>
<td>
</td>
</tr>
</tbody>
</table>
<br>
<br>


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```



```{r cars}
summary(cars)
```



```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
