<head>
<style>
.hr { 
    display: block;
    margin-top: 0.5em;
    margin-bottom: 0.5em;
    margin-left: auto;
    margin-right: auto;
    border-style: inset;
    border-width: 1px;
    width: 60%;
}
.abstract {
    -webkit-column-count: 1; /* Chrome, Safari, Opera */
    -moz-column-count: 1; /* Firefox */
    column-count: 1;
    -moz-column-width: 80%; /* Firefox */
    width: 80%;
    min-width: 300px;
    max-width: 500px;
    height: 50%
}
.newspaper1 {
    -webkit-column-count: 1; /* Chrome, Safari, Opera */
    -moz-column-count: 1; /* Firefox */
    column-count: 1;
    -moz-column-width: 80%; /* Firefox */
    width: 80%;
    min-width: 300px;
    max-width: 600px;
    height: 50%
}
.newspaper2 {
    -webkit-column-count: 2; /* Chrome, Safari, Opera */
    -moz-column-count: 2; /* Firefox */
    column-count: 2;
    -moz-column-width: 80%; /* Firefox */
    width: 80%;
    min-width: 300px;
    max-width: 600px;
    height: 50%
}
.code1 { 
    display: block;
    margin-left: auto;
    margin-right: auto;
    width: 80%;
    max-width: 600px;
}
.code2 {
    -webkit-column-count: 1; /* Chrome, Safari, Opera */
    -moz-column-count: 1; /* Firefox */
    column-count: 1;
    -moz-column-width: 80%; /* Firefox */
    width: 80%;
    min-width: 300px;
    max-width: 600px;
    height: 50%
}
<link rel="stylesheet" href="css/animate.css">
<script src="js/wow.min.js"> </script>
<script> new WOW().init(); </script>
</style>
<script type="text/javascript">
    window.heap=window.heap||[],heap.load=function(e,t){window.heap.appid=e,window.heap.config=t=t||{};var r=t.forceSSL||"https:"===document.location.protocol,a=document.createElement("script");a.type="text/javascript",a.async=!0,a.src=(r?"https:":"http:")+"//cdn.heapanalytics.com/js/heap-"+e+".js";var n=document.getElementsByTagName("script")[0];n.parentNode.insertBefore(a,n);for(var o=function(e){return function(){heap.push([e].concat(Array.prototype.slice.call(arguments,0)))}},p=["addEventProperties","addUserProperties","clearEventProperties","identify","removeEventProperty","setEventProperties","track","unsetEventProperty"],c=0;c<p.length;c++)heap[p[c]]=o(p[c])};
      heap.load("2042091030");
</script>
</head>

<iframe src="https://require.shinyapps.io/require/" style="border: none; width: 100%; height: 770px"></iframe>
<p style="text-align: right;">
Source credit: Yuri @ Aridhia  &nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp; </p><br>
<br><br>

<h4><div class="code1">
<p style="text-align: left;">
ui.R
</p></div>
<h4><div class="code1">
<p style="text-align: left;">
```{r, eval = FALSE}
shinyUI(fluidPage(
  titlePanel("Interactive Neuroimaging Tool using DICOM"),
  helpText("I replicated this interactive tool based on some guide I found online, and it came in handy when I applied for a fellowship at the National Institutes of Health (NIH). Thanks to this tool, I've had the pleasure of speaking with smart scientists for about an hour and a half."),
  fluidRow(
    # Continue column UI element
    column(width = 4,
           h5('Select DICOM file below'),
           uiOutput('fileSelection'),
           #Add slider inputs with arbitrary min/max values 
           sliderInput('slider_x', 'Sagittal Slide', min=1, max=288, value=144),
           sliderInput('slider_y', 'Coronal Slide', min=1, max=288, value=144),
           sliderInput('slider_z', 'Horizontal Slide', min=1, max=22, value=11)
    ),
    
    # Adding column with plot display outputs
    column(width = 7,
           h5('Looking at the brain imaging, it seems the patient has a tumor located on the right hemisphere, mainly in the parietal and temporal region.'),
           tabsetPanel(type = "tabs", 
                       tabPanel("Horizontal", plotOutput("Horizontal", height = "450px",   brush = "plot_brush")), 
                       tabPanel("Sagittal", plotOutput("Sagittal", height = "450px",   brush = "plot_brush")), 
                       tabPanel("Coronal", plotOutput("Coronal", height = "450px",   brush = "plot_brush"))
           )
    )
  )
))

```
</p></div><br><br>

<h4><div class="code1">
<p style="text-align: left;">
server.R
</p></div>
<h4><div class="code1">
<p style="text-align: left;">
```{r, eval = FALSE}
# install.packages(c('oro.dicom','oro.nifti'))
library(oro.dicom)
library(oro.nifti)

shinyServer(function(input, output, session) {
  
  # Select path to DICOM files
  pth <- "Neurohacking_data-0.0/BRAINIX/DICOM/FLAIR/"
  # List folders the path (each folder contains a set of DICOM images)
  dirs <- list.dirs(path = pth, full.names = FALSE, recursive = TRUE)
  
  # Create drop-down menu to select DICOM sets
  output$fileSelection <- renderUI({
    selectInput('fileInput', '', choices = dirs, selected = dirs[2])
  })
  
  dcmImages <- eventReactive(input$fileInput, {
    DICOM_source <-  paste(pth, input$fileInput, sep="")
    print(DICOM_source)
    readDICOM(DICOM_source, verbose = TRUE)
  })
  
  observe({
    # Get length of dcmImages() variables
    print(unlist(lapply(dcmImages(), length)))
  })
  
  niftiVolume <- reactive({
    dicom2nifti(dcmImages(), datatype = 4, rescale = TRUE, reslice = TRUE,
                descrip = NULL)
  })
  
  observe({
    volume <- niftiVolume()
    d <- dim(volume)
    
    # Control the value, min, max, and step.
    # Step size is 2 when input value is even; 1 when value is odd.
    updateSliderInput(session, "slider_x", value = as.integer(d[1]/2), max = d[1])
    updateSliderInput(session, "slider_y", value = as.integer(d[2]/2), max = d[2])
    updateSliderInput(session, "slider_z", value = as.integer(d[3]/2), max = d[3])
  })

  # Add Horizontal, Sagittal and Coronal displays
  output$Horizontal <- renderPlot({
    try(image(niftiVolume(),  z = input$slider_z, plane = "axial", plot.type = "single", col = gray(0:64/64)))
  })
  output$Sagittal <- renderPlot({
    try(image(niftiVolume(),  z = input$slider_x, plane = "sagittal", plot.type = "single", col = gray(0:64/64)))
  })  
  output$Coronal <- renderPlot({
    try(image(niftiVolume(),  z = input$slider_y, plane = "coronal", plot.type = "single", col = gray(0:64/64)))
  })
})
```
</p></div>